The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-03-01 analysis/paper/paper.qmd

## Load required packages, install them if needed
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
  }
  library(package, character.only = TRUE)
}

@@

A total number of `r nrow(emu_theses)` out of `r nrow(theses_all)` were analysed.

@@

# Show thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_count(data = emu_theses, aes(longitude, latitude), color = "red", alpha = 0.7) +
  scale_size_area(max_size = 3) +
  coord_fixed() +
  theme_void()
```

@@

```{r}
# Which theses contain "fabric" in the top 20 most frequently used words?
emu_theses_top_20 %>% 
  filter(word == "fabric")

emu_theses_top_20 %>%
  slice(1:40) %>% 
  ggplot(aes(x = reorder(word, n), y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2)
```

>>>>

## Load required packages, install them if needed
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package,  "http://cran.us.r-project.org")
  }
  library(package, character.only = TRUE)
}

# library(here)
# library(tidyverse)
# library(tidytext)
# library(SnowballC)
# library(tm)
# library(topicmodels)
# library(tidygeocoder)
# library(igraph)
# library(ggraph)

@@

A total number of `r nrow(emu_theses)` out of `r nrow(all_theses)` were analysed.

@@

# Show thesis locations on world map
world <- ggplot2::map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_count(data = emu_theses, aes(longitude, latitude), color = "red", alpha = 0.7) +
  scale_size_area(max_size = 3) +
  coord_fixed() +
  theme_void()
```

@@

```{r}
# Which are the top n most frequently used words in all theses`?
emu_theses_top_20 <- get_top_words_per_corpus(data = emu_theses_words, 
                         top_n = 20, 
                         word_col = "word")
```

<!-- ```{r} -->
<!-- # Which theses contain "fabric" in the top 20 most frequently used words? -->
<!-- emu_theses_top_20 %>%  -->
<!--   filter(word == "fabric") -->

<!-- emu_theses_top_20 %>% -->
<!--   slice(1:40) %>%  -->
<!--   ggplot(aes(x = reorder(word, n), y = n, fill = title)) + -->
<!--   geom_col() + -->
<!--   xlab(NULL) + -->
<!--   coord_flip() + -->
<!--   labs(y = "Count", -->
<!--        x = "Unique words", -->
<!--        title = "Count of unique words found in thesis", -->
<!--        subtitle = "Stop words were removed from the list") + -->
<!--   facet_wrap( ~ title, scales = "free", ncol = 2) -->
<!-- ``` -->
